### 2020-10-09 README.Rmd
Edited Readme

This repository contains the data and code for my paper:

@@

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, domproject, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("DCPollard94/knossoscemeteries")
```
### Licenses

>>>>

This repository contains the data and code for the paper:

@@

You can download the compendium as a zip from from this URL: <https://github.com/DCPollard94/knossoscemeteries/archive/master.zip>

Or you can install this compendium as an R package from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("DCPollard94/knossoscemeteries")
```
### Licenses
